---
title: NOPD v OIPM annual complaints & UOF comparison
output: html_document
---

## Data sources
```{r, include=FALSE}
require(dplyr)

# Complaints
oipm.allegations.csv <- "/media/sf_oipm/code/repo/data_public/clean/allegations_all_clean.csv"
oipm.allegations.all <- read.csv(oipm.allegations.csv, stringsAsFactors = FALSE)

nopd.allegations.csv <- "/media/sf_oipm/code/oipm_nopd_comparison/data.nola.gov/NOPD_Misconduct_Complaints.csv"
nopd.allegations.all <- read.csv(nopd.allegations.csv, stringsAsFactors = FALSE)

# UOF
oipm.uof.csv <- "/media/sf_oipm/code/repo/data_public/clean/uof_clean.csv"
oipm.uof.all <- read.csv(oipm.uof.csv, stringsAsFactors = FALSE)

nopd.uof.csv <- "/media/sf_oipm/code/oipm_nopd_comparison/data.nola.gov/NOPD_Use_of_Force_Incidents.csv"
nopd.uof.all <- read.csv(nopd.uof.csv, stringsAsFactors = FALSE)
```
- Analysis source code [here](https://github.com/marvinmarnold/oipm_nopd_comparison).
- Email sent from NOPD 8/31/18 containing: IAPro misconduct, 2015 comparison, 2017 stats (Sgt Jordan)

## 2017 discrepancies

### Difference between 2017 OIPM and NOPD complaint numbers
```{r, include=FALSE}
oipm.allegations.2017 <- oipm.allegations.all %>% filter(grepl("2017", PIB.Control.Number))
nopd.allegations.2017 <- nopd.allegations.all %>% filter(grepl("2017", Complaint.Tracking.Number))

oipm.allegations.per.complaint.2017 <- oipm.allegations.2017 %>% group_by(PIB.Control.Number) %>% summarise(num.allegs.oipm = n())
nopd.allegations.per.complaint.2017 <- nopd.allegations.2017 %>% group_by(Complaint.Tracking.Number) %>% summarise(num.allegs.nopd = n())

alleg.counts.2017 <- merge(oipm.allegations.per.complaint.2017, nopd.allegations.per.complaint.2017, by.x = 'PIB.Control.Number', by.y = 'Complaint.Tracking.Number', all=TRUE)
alleg.diffs.2017 <- alleg.counts.2017 %>% filter(is.na(num.allegs.oipm) | is.na(num.allegs.nopd) | (num.allegs.oipm != num.allegs.nopd))
```

```{r}
alleg.diffs.2017
```

### Difference between 2017 OIPM and NOPD force numbers
```{r, include=FALSE}
oipm.uof.2017 <- oipm.uof.all %>% filter(grepl("FTN2017", FIT.Number))
nopd.uof.2017 <- nopd.uof.all %>% filter(grepl("FTN2017", PIB.File.Number))

oipm.uof.per.ftn.2017 <- oipm.uof.2017 %>% group_by(FIT.Number) %>% summarise(num.uof.oipm = n())
nopd.uof.per.ftn.2017 <- nopd.uof.2017 %>% group_by(PIB.File.Number) %>% summarise(num.uof.nopd = n())

uof.counts.2017 <- merge(oipm.uof.per.ftn.2017, nopd.uof.per.ftn.2017, by.x = 'FIT.Number', by.y = 'PIB.File.Number', all=TRUE)
uof.diffs.2017 <- uof.counts.2017 %>% filter(is.na(num.uof.oipm) | is.na(num.uof.nopd) | (num.uof.oipm != num.uof.nopd))
```

```{r}
uof.diffs.2017
```

## 2016 discrepancies
### Difference between 2016 OIPM and NOPD complaint numbers
```{r, include=FALSE}
oipm.allegations.2016 <- oipm.allegations.all %>% filter(grepl("2016", PIB.Control.Number))
nopd.allegations.2016 <- nopd.allegations.all %>% filter(grepl("2016", Complaint.Tracking.Number))

oipm.allegations.per.complaint.2016 <- oipm.allegations.2016 %>% group_by(PIB.Control.Number) %>% summarise(num.allegs.oipm = n())
nopd.allegations.per.complaint.2016 <- nopd.allegations.2016 %>% group_by(Complaint.Tracking.Number) %>% summarise(num.allegs.nopd = n())

alleg.counts.2016 <- merge(oipm.allegations.per.complaint.2016, nopd.allegations.per.complaint.2016, by.x = 'PIB.Control.Number', by.y = 'Complaint.Tracking.Number', all=TRUE)
alleg.diffs.2016 <- alleg.counts.2016 %>% filter(is.na(num.allegs.oipm) | is.na(num.allegs.nopd) | (num.allegs.oipm != num.allegs.nopd))
```

```{r}
alleg.diffs.2016
```

### Difference between 2016 OIPM and NOPD force numbers
```{r, include=FALSE}
oipm.uof.2016 <- oipm.uof.all %>% filter(grepl("FTN2016", FIT.Number))
nopd.uof.2016 <- nopd.uof.all %>% filter(grepl("FTN2016", PIB.File.Number))

oipm.uof.per.ftn.2016 <- oipm.uof.2016 %>% group_by(FIT.Number) %>% summarise(num.uof.oipm = n())
nopd.uof.per.ftn.2016 <- nopd.uof.2016 %>% group_by(PIB.File.Number) %>% summarise(num.uof.nopd = n())

uof.counts.2016 <- merge(oipm.uof.per.ftn.2016, nopd.uof.per.ftn.2016, by.x = 'FIT.Number', by.y = 'PIB.File.Number', all=TRUE)
uof.diffs.2016 <- uof.counts.2016 %>% filter(is.na(num.uof.oipm) | is.na(num.uof.nopd) | (num.uof.oipm != num.uof.nopd))
```

```{r}
uof.diffs.2016
```


## 2015 discrepancies
### Difference between 2015 OIPM and NOPD complaint numbers
```{r, include=FALSE}
oipm.allegations.2015 <- oipm.allegations.all %>% filter(grepl("2015", PIB.Control.Number))

nopd.allegations.2015 <- read.csv("/media/sf_oipm/code/oipm_nopd_comparison/data/nopd/2015comparison_IAProReport.csv")

oipm.allegations.per.complaint.2015 <- oipm.allegations.2015 %>% group_by(PIB.Control.Number) %>% summarise(num.allegs.oipm = n())
nopd.allegations.per.complaint.2015 <- nopd.allegations.2015 %>% group_by(PIB.Control.Number) %>% summarise(num.allegs.nopd = n())

alleg.counts.2015 <- merge(oipm.allegations.per.complaint.2015, nopd.allegations.per.complaint.2015, by = 'PIB.Control.Number', all=TRUE)
alleg.diffs.2015 <- alleg.counts.2015 %>% filter(is.na(num.allegs.oipm) | is.na(num.allegs.nopd) | (num.allegs.oipm != num.allegs.nopd))
```

```{r}
alleg.diffs.2015
```

### Difference between 2015 OIPM and NOPD force numbers
```{r, include=FALSE}
oipm.uof.2015 <- oipm.uof.all %>% filter(grepl("FTN2015", FIT.Number))

nopd.uof.2015 <- read.csv("/media/sf_oipm/code/oipm_nopd_comparison/data/nopd/Copy of 2015 UOF data (SQL pull).csv")

oipm.uof.per.ftn.2015 <- oipm.uof.2015 %>% group_by(FIT.Number) %>% summarise(num.uof.oipm = n())
nopd.uof.per.ftn.2015 <- nopd.uof.2015 %>% group_by(filenum) %>% summarise(num.uof.nopd = n())

uof.counts.2015 <- merge(oipm.uof.per.ftn.2015, nopd.uof.per.ftn.2015, by.x = 'FIT.Number', by.y = 'filenum', all=TRUE)
uof.diffs.2015 <- uof.counts.2015 %>% filter(is.na(num.uof.oipm) | is.na(num.uof.nopd) | (num.uof.oipm != num.uof.nopd))
```

```{r}
uof.diffs.2015
```


## Installation
```
devtools::install_github("rmarkdown", "rstudio")
```

